\section{Applications Today}

A decade ago, stationary fixed rate (or occasionally event-driven) data 
reporting applications dominated sensor networks and their research. 
New applications that incorporate mobility, hybrid networking, and 
personal privacy are emerging. A new platform should embrace and enable 
these new opportunities.

\subsection{Human-centric}

The mobile device is a gateway to an embedded networks. Instead of
sending data to a fixed collection point, the network can send directly
to a mobile device, on demand. This enables a person to interact with
the surrounding devices and infrastructure without needing to know a
URL or log into a cloud-based system. Proximity networks provide a degree
of basic, physical security that enables such opportunistic interactions.
Consider the venerable sensor network example of conference rooms. 
Rather than go through a web page or other centralized application, 
you can walk into a room and directly control its lights. 
A data collection gateway for room occupancy,  in addition to streaming
data for durable storage and offline analysis, can make that data
available to your device directly. You can walk into a room, turn on its 
lights, ask it how long it is free for, and see what other rooms are free.

Because these interactions are human-centric, they require low latency and
are highly bursty -- two performance properties unimportant in the 
dominant network model of the past decade. These low-latency interactions
are more than event notifications or alarms. They can involve significant
queries and exchanges of data. Furthermore, becuase they involve mobile
devices, existing approaches of long-term link estimation are of limited use.
These new application requirements will force us to rethink the tradeoffs
between latency, storage, energy, snooping, and how an operating system will
support them.

\subsection{Perpetual Networks}

Energy harvesting and low-power peripherals will finally enable a
long-term goal of the sensor network community: perpetual networks. Imagine
an iBeacon that, once installed, could possibly run forever. Or smoke detectors that need no battery replacements. If the world will be filled with
thousands of smart objects per person, energy must recede to be a non-issue
for almost all of them.

We still can't predict the weather, and so we of course also still can't 
predict the performance of a solar cell. This means an operating system
is stuck between two big unknowns: the future energy available as well as
the potential energy needs from bursty, human-centric interactions. For
an embedded device to be truly perpetual, it must scale its behavior and
perfomance based on these two factors, optimizing how it uses its energy
as needed. 


\sub


\smallskip\noindent
\textbf{How Applications Drive Platforms.}

\glipsum[1]

\smallskip\noindent
\textbf{Privacy and Proximity in Networks.}
Interactions between PANs (centered around a user’s mobile phone)
and proximity applications such as iBeacons happen in public, with
never-seen-before peers. This presents a dual security and privacy problem. On
the one hand, connections between the PAN and proximity device must be
confidential and authentic -- e.g. payments.
On the other hand, casual interactions with
proximity devices must not enable ubiquitous tracking of users. Unfortunately,
confidential and authentic communication and anonymity are difficult to
achieve simultaneously.
%
Operating systems can play a role in addressing these issues, for example by coordinating
security features in the BLE stack with application specific knowledge.

%% Too detailed an example for a poster abstract
%
% For example, we propose a new mechanism -- Address Isolation -- that leverages
% Resolvable Private Addresses in BLE to expose multiple private identities from
% the same end-user device. Resolable Private Addresses are BLE device addresses
% derived from a public random value and a shared secret between peers. This
% allows peers to identify each other through addresses that appear random to
% nearby devices that do not share the secret. Address Isolation uses this BLE
% mechanism to expose multiple identities (each resolvable by, e.g. a single
% point-of-sale operator, but anonymous to everyone else) at the OS level, by
% coordinating when each identity should be used with applications. For example,
% in the point-of-sale scenario, the application loads a shared secret key with
% a point-of-sale operator (e.g. Wal-Mart) at application install time, and
% tells the operating system to use the identity based on that key upon user
% interaction, such as initiating a payment.

